### 2016-02-04 mcmc.tex
phil

\begin{document}\sloppy\sloppypar\raggedbottom\thispagestyle{plain}%
%
\section*{Data analysis recipes:\\ \chaptertitle\footnotemark}
%
\footnotetext{%
    The notes begin on page~\pageref{note:first}, including the
    license\note{\label{note:first}
        Copyright 2013, 2014, 2015, 2016 the authors (OMG this took us a long time).
        This work is licensed under a
        \href{http://creativecommons.org/licenses/by-nc-nd/3.0/deed.en\_US}{%
            Creative Commons Attribution-NonCommercial-NoDerivs 3.0 Unported
            License}.}
    and the acknowledgements\note{%
        We would like to thank
          Jo Bovy (IAS),
          Brendon Brewer (Auckland),
          Jonathan Goodman (NYU),
          Fengji Hou (NYU),
          Dustin Lang (CMU), and
          Iain Murray (Edinburgh)
        for valuable advice and comments over the years.
        This project benefitted from various research grants, especially
          NSF grants AST-0908357, IIS-1124794, and AST-1517237,
          NASA grant NNX12AI50G,
          and the The Moore-Sloan Data Science Environment at NYU.}
}

>>>>

\begin{document}\sloppy\sloppypar\raggedbottom\thispagestyle{plain}%
%
\section*{Data analysis recipes:\\ \chaptertitle\footnotemark}
%
\footnotetext{%
    The notes begin on page~\pageref{note:first}, including the
    license\note{\label{note:first}
        Copyright 2013, 2014, 2015, 2016 the authors (OMG this took us a long time).
        This work is licensed under a
        \href{http://creativecommons.org/licenses/by-nc-nd/3.0/deed.en\_US}{%
            Creative Commons Attribution-NonCommercial-NoDerivs 3.0 Unported
            License}.}
    and the acknowledgements\note{%
        We would like to thank
          Jo Bovy (IAS),
          Brendon Brewer (Auckland),
          Jonathan Goodman (NYU),
          Fengji Hou (NYU),
          Dustin Lang (CMU),
          Phil Marshall (KIPAC), and
          Iain Murray (Edinburgh)
        for valuable advice and comments over the years.
        This project benefitted from various research grants, especially
          NSF grants AST-0908357, IIS-1124794, and AST-1517237,
          NASA grant NNX12AI50G,
          and the The Moore-Sloan Data Science Environment at NYU.}
}
